% Intended LaTeX compiler: pdflatex
\documentclass[12pt,letterpaper]{shillcv}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
                              \usepackage[margin=1in]{geometry}
\usepackage{tabularx}
\setlength{\parindent}{0pt}
\usepackage{doi}
\author{Spencer A. Hill}
\date{\today}
\title{Publications}
\hypersetup{
 pdfauthor={Spencer A. Hill},
 pdftitle={Publications},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.2)},
 pdflang={English}}
\begin{document}

\maketitle


\section*{In preparation}
\label{sec:org1499a6e}
\begin{enumerate}
\item \textbf{Hill, Spencer A.}, Simona Bordoni, and Jonathan L. Mitchell.  "Meridional
variations in radiative convective equilibrium tropopause height and their
influence on axisymmetric Hadley cells."  In preparation for submission to
\emph{Journal of the Atmospheric Sciences}.
\item \textbf{Hill, Spencer A.} and Natalie J. Burls.  "Mechanisms of poleward energy
transport changes under CO\(_2\) forcing and in the Pliocene."  In
preparation for submission to \emph{Journal of Advances in Modeling Earth
Systems}.
\end{enumerate}
\section*{Submitted/under review/in revision}
\label{sec:org79cbf59}
\begin{enumerate}
\item \textbf{Hill, Spencer A.} "CQE, MSE, ITCZ, or all three? On theories of monsoon
rainfall and its response to climate change."  Under review, \emph{Current Climate
Change Reports}.
\item \textbf{Hill, Spencer A.}, Simona Bordoni, and Jonathan L. Mitchell.  "Axisymmetric
constraints on cross-equatorial Hadley cell extent."  Revised for \emph{Journal of
the Atmospheric Sciences}.
\end{enumerate}
\section*{Peer-reviewed}
\label{sec:org7281a6c}
\begin{enumerate}
\item (2018) \textbf{Hill, Spencer A.}, Juan M. Lora, Norris Khoo, Sean P. Faulk, and
Jonathan M.  Aurnou.  "Affordable rotating fluid demonstrations for
geoscience education: The \emph{DIYnamics} project."  \emph{Bulletin of the
American Meteorological Society}, \textbf{99}, 2529-2538.  doi:
\href{https://doi.org/10.1175/BAMS-D-17-0215.1}{10.1175/BAMS-D-17-0215.1}.
\item (2018) \textbf{Hill, Spencer A.}, Yi Ming, and Ming Zhao.  "Robust responses of the
Sahelian hydrological cycle to global warming."  \emph{Journal of
Climate}, \textbf{31}, 9793-9814.  doi: \href{https://doi.org/10.1175/JCLI-D-18-0238.1}{10.1175/JCLI-D-18-0238.1}.
\item (2018) Smyth, Jane, \textbf{Spencer A. Hill}, and Yi Ming.  "Simulated responses of
the West African monsoon and zonal-mean tropical precipitation to early
Holocene orbital forcing."  \emph{Geophysical Research Letters}, \textbf{45},
12,049-12,057.  doi: \href{https://doi.org/10.1029/2018GL080494}{10.1029/2018GL080494}.
\item (2017) \textbf{Hill, Spencer A.}, Yi Ming, Isaac M. Held, and Ming Zhao.  "A moist
static energy budget-based analysis of the Sahel rainfall response to uniform
oceanic warming."  \emph{Journal of Climate}, \textbf{30}, 5637-5660.  doi:
\href{https://doi.org/10.1175/JCLI-D-16-0785.1}{10.1175/JCLI-D-16-0785.1}.
\item (2017) Brown, Patrick T., Yi Ming, Wenhong Li, and \textbf{Spencer A. Hill}.  "Change
in the magnitude and mechanisms of unforced low-frequency surface temperature
variability in a warmer climate."  \emph{Nature Climate Change}, \textbf{7}, 743-748.
doi: \href{https://doi.org/10.1038/nclimate3381}{10.1038/nclimate3381}.
\item (2017) Jeevanjee, Nadir, Pedram Hassanzadeh, \textbf{Spencer A. Hill}, and Aditi
Sheshadri.  "A perspective on climate model hierarchies."  \emph{Journal
of Advances in Modeling Earth Systems}, \textbf{9}, 1760-1771.  doi: \href{https://doi.org/10.1002/2017MS001038}{10.1002/2017MS001038}.
\item (2015) \textbf{Hill, Spencer A.}, Yi Ming, and Isaac M. Held.  "Mechanisms of forced
tropical meridional energy flux change."  \emph{Journal of Climate}, \textbf{28},
1725-1742.  doi: \href{http://dx.doi.org/10.1175/JCLI-D-14-00165.1}{10.1175/JCLI-D-14-00165.1}.
\begin{itemize}
\item Corrigendum: \url{https://dx.doi.org/10.1175/JCLI-D-16-0485.1}.
\end{itemize}
\item (2012) \textbf{Hill, Spencer A.} and Yi Ming.  "Nonlinear climate response to regional
brightening of tropical marine stratocumulus."  \emph{Geophysical Research Letters},
\textbf{39}, L15707, 5 pp. doi:
\href{http://dx.doi.org/10.1029/2012GL052064}{10.1029/2012GL052064}.
\end{enumerate}
\section*{PhD thesis}
\label{sec:org745cab9}
(2016) \textbf{Hill, Spencer A.} "Energetic and hydrological responses of Hadley
circulations and the African Sahel to sea surface temperature perturbations."
PhD Thesis, Princeton University Program in Atmospheric and Oceanic Sciences.
\section*{Non peer-reviewed}
\label{sec:orgadb33a5}
\begin{enumerate}
\item (2017) \textbf{Hill, Spencer A.} and Spencer K. Clark.  "What’s needed for the Future
of AOS Python? Tools for Automating AOS Data Analysis and Management."
Invited guest blog post on "PyAOS" blog.  URL:
\url{http://pyaos.johnny-lin.com/?p=1546}.
\item (2012) \textbf{Hill, Spencer A.}  "A head in the clouds elucidates climate" (book
review of \href{http://press.princeton.edu/titles/9773.html}{\emph{Atmosphere, Clouds, and Climate}} by David Randall). \emph{Science}, \textbf{337},
1 pp., doi: \href{http://dx.doi.org/10.1126/science.1225615}{10.1126/science.1225615}.
\end{enumerate}
\section*{Software}
\label{sec:org57f4b45}
\begin{enumerate}
\item (2018) \textbf{Hill, Spencer A.} and Spencer Clark.  "\texttt{aospy}: automated climate
data analysis and management."  Version 0.3.1.  \url{https://aospy.readthedocs.io}.
doi: \href{https://doi.org/10.5281/zenodo.1490928}{10.5281/zenodo.1490928}.
\item (2016) Hoyer, Stephan et al.  "xarray: v0.8.0."  doi: \href{https://doi.org/10.5281/zenodo.59499}{10.5281/zenodo.59499}.
\end{enumerate}
\end{document}